Title

### 2013-03-27 inc/model_results/spacecharge/spacecharge.tex
tweaks

This trend is clearly evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) as a function of the number of electrons in the pulse after a propagation distance of 15cm.
The pulses are not accelerated but rather start with a velocity of $c/3$ (where $c$ is the speed of light in a vacuum), initial width of 1 mm, HW1/eM pulse duration 1 ps, have the initial momentum chirps $\gamma_{\smallT} = \gamma{z} = 0 $ and momentum uncertainties related to an excess photoemission energy of $\Delta E = $ 0.5 eV.
These naive conditions are needed to isolate the behavior of a propagating pulse from its creation environment.
The simulations, clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the electron pulse divergence and its temporal broadening rate are both proportional to $\Delta E^{1/2}$.

>>>>

This trend is clearly evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) as a function of the number of electrons in the pulse after a propagation distance of 15cm.
The pulses are not accelerated but rather start with a velocity of $c/3$ (where $c$ is the speed of light in a vacuum), initial width of 1 mm, HW1/eM pulse duration 1 ps, have the initial momentum chirps $\gamma_{\smallT} = \gamma{z} = 0 $ and momentum uncertainties related to an excess photoemission energy of $\Delta E = $ 0.5 eV.
These naive conditions are needed to isolate the behavior of a propagating pulse from its creation environment.
The simulations clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the electron pulse divergence and its temporal broadening rate are both proportional to $\Delta E^{1/2}$.
